\cvsection{Employment}
\honortitlestyle{References upon request}
\begin{cventries}
  \cventry%
    {Imaging and Color Science Intern}
    {Ricoh USA, Inc.}
    {Boulder, Colorado}
    {May 2018 --- August 2018}
    {%
      \begin{cvitems}
         \item Developed the backend software to capture images in real-time
               (tested up to 3.6 GB/s) and send it directly to the GPU using C++
               and OpenGL.\@
         \item Created a GUI in Qt Creator to control the camera and paper drum to save
               images of various size or stream them to the monitor in real-time.
      \end{cvitems}
    }
  \cventry%
    {Software Engineering Intern}
    {SEAKR Engineering}
    {Centennial, Colorado}
    {May 2017 --- August 2017}
    {%
      \begin{cvitems}
         \item Ported a proprietary C++ software package from VxWorks to Linux.
         The software also moved to a new architecture, which required more
         rewritten code.
         \item Installed PetaLinux on the flash memory of a MicroZed development board.
      \end{cvitems}
    }
  \cventry%
    {Warehouse Worker}
    {MasterCraft Truck Equipment, Inc.}
    {Englewood, Colorado}
    {Summers, 2015 --- 2016}
    {%
      \begin{cvitems}
         \item Learned about small scale installation processes.
         \item Received and processed 2--3 large shipments per day.
         \item Delivered the finished vehicle to the customer.
      \end{cvitems}
    }
%  \cventry
%    {Retail Salesman}
%    {Destination Disc, LLC}
%    {Conifer, Colorado}
%    {Summers, 2013 - 2014}
%    {
%      \begin{cvitems}
%         \item Interacted with 150 customers a day
%         \item Improved the product sales and management system
%      \end{cvitems}
%    }
\end{cventries}
